The Astropy Project

### 2017-11-22 main.tex
tweak wording

The released versions of the \astropypkg core package are available from several
of the \python distributions for scientific computing (e.g.,
\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
(PyPI).\footnote{See the installation documentation for more information:
\url{http://docs.astropy.org/en/stable/install.html}}

>>>>

The released versions of the \astropypkg core package are available from several
of the \python distributions for scientific computing (e.g.,
\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
(PyPI).\footnote{See the installation documentation for more information:
\url{http://docs.astropy.org/en/stable/install.html}}
Effort has been made to make \astropypkg available and easily installable across
all platforms; the package is constantly tested on different platforms as part
of our suite of continuous integration tests.
